### 2015-04-13 contract-language.tex
Added references to the technical report

The theorem states that if a data store correctly enforces $\scc$, $\ccc$, and
$\ecc$ contracts in all well-formed executions, then the same store, extended
with the classification scheme shown in Figure~\ref{sem:classify}, can enforce
all well-formed \name contracts. The proof of the theorem is given in the
supplementary material\footnote{The supplementary material also provides the
concrete reduction rules for enforcing the consistency classes.}.

>>>>

The theorem states that if a data store correctly enforces $\scc$, $\ccc$, and
$\ecc$ contracts in all well-formed executions, then the same store, extended
with the classification scheme shown in Figure~\ref{sem:classify}, can enforce
all well-formed \name contracts. The proof of the theorem is given in the
accompanying technical report~\cite{techrep} \footnote{The technical report also
provides the concrete reduction rules for enforcing the consistency classes.}.
